---
pagetitle: "Research"
title: ""
page-layout: full
toc: false
comments: false
---

::: {.hero-section}
# Research
Advancing biomedical research through AI-driven approaches to solve complex health challenges and improve patient outcomes.
:::

::: {.main-content}

```{r}
#| echo: false
#| message: false
#| warning: false

# Load required libraries
library(yaml)

# Read research data
research_data <- yaml::read_yaml("../_data/research.yml")

# Function to render research area card
render_research_area <- function(area) {
  paste0(
    '<div class="research-area-card">',
    '<div class="research-icon">', area$icon, '</div>',
    '<div class="research-content">',
    '<h3>', area$title, '</h3>',
    '<p>', area$description, '</p>',
    '</div>',
    '</div>'
  )
}

# Function to render project card
render_project <- function(project, type = "current") {
  # Create status badge
  status_class <- tolower(gsub(" ", "-", project$status))

  # Create tags
  tags_html <- ""
  if (!is.null(project$tags) && length(project$tags) > 0) {
    tags_list <- paste0("- ", project$tags, collapse = "\n")
    tags_html <- paste0('<div class="project-tags">\n', tags_list, '\n</div>')
  }

  # Create funding info
  funding_html <- ""
  if (!is.null(project$funding_source)) {
    funding_html <- paste0(
      '<p><strong>Funding:</strong> ', project$funding_source,
      if (!is.null(project$funding_amount)) paste0(' (', project$funding_amount, ')') else '',
      '<br>',
      '<strong>Duration:</strong> ', project$duration, '<br>',
      '<strong>Role:</strong> ', project$role, '</p>'
    )
  }

  # Create publications section for completed projects
  publications_html <- ""
  if (!is.null(project$publications) && length(project$publications) > 0) {
    pubs_list <- paste0("- ", project$publications, collapse = "\n")
    publications_html <- paste0('<div class="project-publications"><strong>Related Publications:</strong>\n', pubs_list, '\n</div>')
  }

  # Create submission date for proposed projects
  submission_html <- ""
  if (!is.null(project$submission_date)) {
    submission_html <- paste0('<p><strong>Submission Date:</strong> ', project$submission_date, '</p>')
  }

  # Determine card class
  card_class <- "project-card"
  if (!is.null(project$featured) && project$featured) {
    card_class <- paste(card_class, "featured")
  }
  card_class <- paste(card_class, status_class)

  return(paste0(
    '<div class="', card_class, '">',
    '<div class="project-status">', project$status, '</div>',
    '<div class="project-content">',
    '<h3>', project$title, '</h3>',
    funding_html,
    submission_html,
    '<p>', project$description, '</p>',
    tags_html,
    publications_html,
    '</div>',
    '</div>'
  ))
}

# Function to render collaboration
render_collaboration <- function(collab) {
  type_class <- tolower(gsub(" ", "-", collab$type))

  # Create a compact single-line format
  paste0(
    '<div class="collaboration-item ', type_class, '">',
    '<div class="collab-institution">',
    '<strong>', collab$institution, '</strong>',
    '<span class="collab-type-badge">', collab$type, '</span>',
    '</div>',
    '<div class="collab-details">',
    '<span class="collab-project">', collab$project, '</span>',
    ' • <span class="collab-role">', collab$role, '</span>',
    ' • <span class="collab-duration">', collab$duration, '</span>',
    '</div>',
    '</div>'
  )
}
```

::: {.research-areas-section}
## Research Areas

```{r}
#| echo: false
#| results: asis

cat('<div class="research-areas-grid">')
for (area in research_data$research_areas) {
  cat(render_research_area(area))
}
cat('</div>')
```
:::

## Current Projects

```{r}
#| echo: false
#| results: asis

cat('<div class="projects-grid">')
for (project in research_data$current_projects) {
  cat(render_project(project, "current"))
}
cat('</div>')
```

## Completed Projects

```{r}
#| echo: false
#| results: asis

cat('<div class="projects-grid">')
for (project in research_data$completed_projects) {
  cat(render_project(project, "completed"))
}
cat('</div>')
```

## Proposed Projects

```{r}
#| echo: false
#| results: asis

cat('<div class="projects-grid">')
for (project in research_data$proposed_projects) {
  cat(render_project(project, "proposed"))
}
cat('</div>')
```

## Research Collaborations

```{r}
#| echo: false
#| results: asis

cat('<div class="collaborations-list">')
for (collab in research_data$collaborations) {
  cat(render_collaboration(collab))
}
cat('</div>')
```

<style>
.hero-section {
  text-align: center;
  padding: 3rem 1rem;
  margin-bottom: 2rem;
}

.hero-section h1 {
  font-size: 3rem;
  margin-bottom: 1rem;
  color: var(--text-primary);
}

.hero-section p {
  font-size: 1.2rem;
  color: var(--text-secondary);
  max-width: 600px;
  margin: 0 auto;
}

.main-content {
  max-width: 1200px;
  margin: 0 auto;
  padding: 0 1rem;
}

@media (max-width: 768px) {
  .hero-section h1 {
    font-size: 2rem;
  }
}
</style>
