---
format:
  pdf:
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 11pt
    geometry:
      - margin=1in
      - heightrounded
    include-in-header:
      - preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r}
#| name: setup
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
  fig.path = "figs/",
  fig.width = 7.252,
  fig.height = 4,
  comment = "#>",
  fig.retina = 3
)

source("functions.R")

# Store IDs
gscholar_id <- '9_K4ekoAAAAJ'
gscholar_page <- paste0("https://scholar.google.com/citations?user=", gscholar_id)
```

\par\centering{\LARGE{Md. Jubayer Hossain}}
\par\centering{Department of Public Health}
\vspace{-5pt}
\par\centering{Daffodil International University}
\vspace{-5pt}
\par\centering{Daffodil Smart City}
\vspace{-5pt}
\par\centering{Birulia, Savar, Dhaka-1216, Bangladesh}
\vspace{-5pt}
\par\centering{{\large\Telefon} +8801662345906}
\vspace{-5pt}
\par\centering{{\large\Letter} hossainmj.me@gmail.com}
\vspace{-5pt}
\par\centering{\href{http://www.mdjubayerhossain.com}{www.mdjubayerhossain.com}}

\vspace{-10pt}

# Academic Appointments

```{r}
#| results: asis
get_cv_sheet('academics') %>%
  fill(start_date, end_date, role, institution, where) %>%
  mutate(
    date = ifelse(
      is.na(end_date) | end_date == "Present",
      paste0(format(start_date, "%b %Y"), " - Present"),
      paste0(format(start_date, "%b %Y"), " - ", end_date)
    )
  ) %>%
  make_cv_entries(date, role, institution, where, details)
```

# Leadership Experience

```{r}
#| results: asis
get_cv_sheet('leadership') %>%
  fill(start_date, end_date, role, institution, where) %>%
  mutate(
    date = ifelse(
      is.na(end_date) | end_date == "Present",
      paste0(format(start_date, "%b %Y"), " - Present"),
      paste0(format(start_date, "%b %Y"), " - ", end_date)
    )
  ) %>%
  make_cv_entries(date, role, institution, where, details)
```

# Community Engagement

```{r}
#| results: asis
get_cv_sheet('community') %>%
  fill(start_date, end_date, role, institution, where) %>%
  mutate(
    date = ifelse(
      is.na(end_date) | end_date == "Present",
      paste0(format(start_date, "%b %Y"), " - Present"),
      paste0(format(start_date, "%b %Y"), " - ", end_date)
    )
  ) %>%
  make_cv_entries(date, role, institution, where, details)
```

# Education & Training

```{r}
#| results: asis
get_cv_sheet('education') %>%
  make_cv_entries(year, degree, institution, where, details)
```

# Technical Skills 
- **Programming Languages**: Python, R, Julia, SQL, Bash, JavaScript
- **Bioinformatics**: Bulk RNA-Seq, Single-Cell RNA-Seq, Spatial Transcriptomics, Multi-omics
- **Workflow Management & Reproducibility**: Nextflow (DSL2), nf-core, Docker, Singularity, Git, GitHub
- **AI in Biology**: Scikit-learn, PyTorch, RDkit, DeepChem
- **HPC & Cluster Computing**: SLURM (sbatch, sarray), Nextflow DSL2 with SLURM executor for scalable reusable pipelines
- **Cloud**: AWS S3, Google Cloud Storage for large genomic datasets


# Research Interests
- **Bioinformatics**: Integrative analysis of bulk RNA-seq, single-cell RNA-seq, and spatial transcriptomics to identify robust immunological biomarkers and therapeutic targets within tumor microenvironments;

- **AI in Biology**: Deep learning applications in single-cell genomics, particularly for data integration and cell type annotation.

\vspace{-15pt}

# Teaching Interests
- **Programming \& Data Analytics**: Programming in R and Python; exploratory data analysis; data visualization; reproducibility.
- **Bioinformatics**: Scalable, reproducible computational pipelines for single-cell, spatial, and bulk transcriptomics to elucidate complex disease biology (Bash, Nextflow, Docker).  
- **AI in Biology**: Applying deep learning frameworks to single-cell genomics data for high-accuracy predictive modeling. 

# Publications 

  \apptocmd{\tightlist}{\setlength{\itemsep}{4pt}}{}{}

ORCID: \href{https://orcid.org/0000-0001-9323-4997}{0000-0001-9323-4997} | [Google Scholar Profile](https://scholar.google.com/citations?user=9_K4ekoAAAAJ&hl=en&authuser=5)

\underline{Underline} indicates mentee; ** undergraduate student; * corresponding 

## A. Journal Articles
```{r}
pubs <- get_cv_sheet('pubs') %>%
  mutate(
    journal  = ifelse(is.na(journal), '', paste0('_', journal, '_.')),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    doi      = ifelse(
               is.na(doi), '',
               paste0('DOI: [', doi, '](', 'https://doi.org/', doi, ')')),
    url_repo = ifelse(is.na(url_repo), '', paste0('[', url_repo, '](', url_repo, ')')),
    year     = paste0("(", year, ")"),
    title    = enquote(title),
    citation = paste(author, year, title, journal, number, doi, url_repo)
  ) %>% 
  arrange(desc(pub_date))
```

```{r}
#| results: asis

make_ordered_list_filtered(pubs, "peer_reviewed")
```

## B. GBD Contributions 
```{r}
#| results: asis

make_ordered_list_filtered(pubs, "gbd")
```


## C. Papers Under Review

```{r}
#| results: asis
 
make_ordered_list_filtered(pubs, "under_review")
```

## D. Working Papers

```{r}
#| results: asis
 
make_ordered_list_filtered(pubs, "working")
```

# Presentations

```{r}
presentations <- get_cv_sheet('presentations') %>%
  arrange(desc(date)) %>% 
  mutate(
    with = ifelse(is.na(with), '', paste0(', with ', with)),
    title = paste0(enquote(title), with),
    title = ifelse(is.na(series), title, paste(title, series, sep = '. ')),
    date = paste0(format(as.Date(date), format = "%b %d, %Y"), '.'),
    citation = paste(title, host, location, date, sep = '. ')
  )

presentation_counts <- presentations %>%
  count(category) %>%
  left_join(data.frame(
    category = c(
      "invited", "panelist", "conference", "poster", "organizer", "discussant"
    ),
    order = seq(6)
  )) %>%
  mutate(
    category = str_to_title(category),
    category = ifelse(category == 'Invited', 'Invited Speaker', category),
    category = ifelse(category == 'Panelist', 'Invited Panelist', category),
    category = ifelse(category == 'Conference', 'Conference Presentation', category),
    category = ifelse(category == 'Poster', '\\newline Poster Presentation', category),
    cite = paste0(category, ' (', n, ')')
  ) %>%
  arrange(order) %>%
  pull(cite) %>%
  paste(collapse = ', ')
```

## A. Invited Speaker

```{r}
#| results: asis

make_ordered_list_filtered(presentations, "invited")
```

## B. Conference Presentations

```{r}
#| results: asis

make_ordered_list_filtered(presentations, "conference")
```

## C. Posters

```{r}
#| results: asis

make_ordered_list_filtered(presentations, "poster")
```

# Teaching & Education

## A. Courses Taught

```{r}
df <- get_cv_sheet('classes') %>%
    mutate(
        course = paste0(number, ": ", name),
        num = paste(responses, '/', enrolled),
        score = paste(inst_mean, '/', dept_mean),
        semester = ifelse(semester == 'S20', 'S20$^†$', semester)
    ) %>%
    select(
        `Cohort.` = semester,
        Course = course,
        Level = level,
        `N. Resp. / N. Enrolled` = num,
        `Instr. FCE* / Dept Mean` = score
    )

df %>%
    kbl(booktabs = TRUE, escape = FALSE, linesep = "") %>%
    column_spec(4, width = "1.8cm") %>%
    column_spec(5, width = "2cm") %>%
    footnote(
        symbol = c(
            "Faculty Course Evaluations (FCE) are scored by students (1 = worst, 5 = best)."
        )
    )
```

## B. Workshops

```{r}
teaching <- get_cv_sheet('teaching') %>%
    arrange(desc(date)) %>%
    mutate(
        with = ifelse(is.na(with), '', paste0(', with ', with)),
        title_text = paste0(enquote(title), with),
        title = ifelse(is.na(url), title_text, paste0("[", title_text, "](", url, ")")),
        date = paste0(format(as.Date(date), format = "%b %d, %Y"), "."),
        citation = paste(title, host, location, date, sep = '. ')
    )
```

```{r}
#| results: asis

make_ordered_list_filtered(teaching, "workshop")
```

# Media Coverage
<!-- Set spacing in between list -->
\apptocmd{\tightlist}{\setlength{\itemsep}{2pt}}{}{}

```{r}
media <- get_cv_sheet('media') %>%
  arrange(desc(date)) %>%
  mutate(
      date = format(date, format = "%b %d, %Y"),
      outlet = paste0("**", outlet, "**"),
      citation = paste0(date, ", ", outlet, ": ", post, '.')
  )

media_counts <- media %>%
  count(type) %>% 
  mutate(
    type = str_replace_all(type, '_', ' '),
    type = str_to_title(type), 
    type = ifelse(type == 'Tv', 'TV', type), 
    type = ifelse(type == 'Government', 'Federal Government', type), 
    cite = paste0(type, ' (', n, ')'),
    has_press = str_detect(type, 'Press')
  ) %>%
  arrange(!has_press) %>%
  pull(cite) %>%
  paste(collapse = ', ')
```


```{r}
#| results: asis

media %>%
  filter(highlight == 1) %>%
  pull(citation) %>%
  make_ordered_list()
```


# References

\noindent
\begin{minipage}[t]{0.32\linewidth}
\textbf{Dr. Syeda Tasneem Towhid} \\
Associate Professor \\
Department of Microbiology \\
Jagannath University \\
Dhaka, Bangladesh \\
\href{mailto:towhidst@mib.jnu.ac.bd}{towhidst@mib.jnu.ac.bd}
\end{minipage}
\hfill
\begin{minipage}[t]{0.32\linewidth}
\textbf{Dr. Md. Salequl Islam} \\
Professor \\
Department of Microbiology \\
Jahangirnagar University \\
Dhaka, Bangladesh \\
\href{mailto:salequl@juniv.edu}{salequl@juniv.edu}
\end{minipage}
\hfill
\begin{minipage}[t]{0.32\linewidth}
\textbf{Dr. Zeba Islam Seraj} \\
Director, cBLAST \\
University of Dhaka \\
Dhaka, Bangladesh \\
\href{mailto:zebai@du.ac.bd}{zebai@du.ac.bd}
\end{minipage}
