---
format:
  pdf:
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 10pt
    geometry:
      - margin=1in
      - heightrounded
    include-in-header:
      - preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r}
#| name: setup
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
  fig.path = "figs/",
  fig.width = 7.252,
  fig.height = 4,
  comment = "#>",
  fig.retina = 3
)

source("functions.R")

# Store IDs
gscholar_id <- '9_K4ekoAAAAJ'
gscholar_page <- paste0("https://scholar.google.com/citations?user=", gscholar_id)
```

\par\centering{\LARGE{Md. Jubayer Hossain}}
\par\centering{Department of Public Health}
\vspace{-5pt}
\par\centering{Daffodil International University}
\vspace{-5pt}
\par\centering{Daffodil Smart City}
\vspace{-5pt}
\par\centering{Birulia, Savar, Dhaka-1216, Bangladesh}
\vspace{-5pt}
\par\centering{{\large\Telefon} +8801662345906}
\vspace{-5pt}
\par\centering{{\large\Letter} hossainmj.me@gmail.com}
\vspace{-5pt}
\par\centering{\href{http://www.mdjubayerhossain.com}{www.mdjubayerhossain.com}}

# Publications 

  \apptocmd{\tightlist}{\setlength{\itemsep}{4pt}}{}{}

ORCID: \href{https://orcid.org/0000-0001-9323-4997}{0000-0001-9323-4997} | [Google Scholar Profile](https://scholar.google.com/citations?user=9_K4ekoAAAAJ&hl=en&authuser=5)

\underline{Underline} indicates mentee; ** undergraduate student; * corresponding 

## A. Journal Articles
```{r}
pubs <- get_cv_sheet('pubs') %>%
  mutate(
    journal  = ifelse(is.na(journal), '', paste0('_', journal, '_.')),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    doi      = ifelse(
               is.na(doi), '',
               paste0('DOI: [', doi, '](', 'https://doi.org/', doi, ')')),
    url_repo = ifelse(is.na(url_repo), '', paste0('[', url_repo, '](', url_repo, ')')),
    year     = paste0("(", year, ")"),
    title    = enquote(title),
    citation = paste(author, year, title, journal, number, doi, url_repo)
  ) %>% 
  arrange(desc(pub_date))
```

```{r}
#| results: asis

make_ordered_list_filtered(pubs, "peer_reviewed")
```

## B. GBD Contributions 
```{r}
#| results: asis

make_ordered_list_filtered(pubs, "gbd")
```


## C. Papers Under Review

```{r}
#| results: asis
 
make_ordered_list_filtered(pubs, "under_review")
```

## D. Working Papers

```{r}
#| results: asis
 
make_ordered_list_filtered(pubs, "working")
```

# Presentations

```{r}
presentations <- get_cv_sheet('presentations') %>%
  arrange(desc(date)) %>% 
  mutate(
    with = ifelse(is.na(with), '', paste0(', with ', with)),
    title = paste0(enquote(title), with),
    title = ifelse(is.na(series), title, paste(title, series, sep = '. ')),
    date = paste0(format(as.Date(date), format = "%b %d, %Y"), '.'),
    citation = paste(title, host, location, date, sep = '. ')
  )

presentation_counts <- presentations %>%
  count(category) %>%
  left_join(data.frame(
    category = c(
      "invited", "panelist", "conference", "poster", "organizer", "discussant"
    ),
    order = seq(6)
  )) %>%
  mutate(
    category = str_to_title(category),
    category = ifelse(category == 'Invited', 'Invited Speaker', category),
    category = ifelse(category == 'Panelist', 'Invited Panelist', category),
    category = ifelse(category == 'Conference', 'Conference Presentation', category),
    category = ifelse(category == 'Poster', '\\newline Poster Presentation', category),
    cite = paste0(category, ' (', n, ')')
  ) %>%
  arrange(order) %>%
  pull(cite) %>%
  paste(collapse = ', ')
```

## A. Invited Speaker

```{r}
#| results: asis

make_ordered_list_filtered(presentations, "invited")
```

## B. Conference Presentations

```{r}
#| results: asis

make_ordered_list_filtered(presentations, "conference")
```

## C. Posters

```{r}
#| results: asis

make_ordered_list_filtered(presentations, "poster")
```

# Media Coverage
<!-- Set spacing in between list -->
\apptocmd{\tightlist}{\setlength{\itemsep}{2pt}}{}{}

```{r}
media <- get_cv_sheet('media') %>%
  arrange(desc(date)) %>%
  mutate(
      date = format(date, format = "%b %d, %Y"),
      outlet = paste0("**", outlet, "**"),
      citation = paste0(date, ", ", outlet, ": ", post, '.')
  )

media_counts <- media %>%
  count(type) %>% 
  mutate(
    type = str_replace_all(type, '_', ' '),
    type = str_to_title(type), 
    type = ifelse(type == 'Tv', 'TV', type), 
    type = ifelse(type == 'Government', 'Federal Government', type), 
    cite = paste0(type, ' (', n, ')'),
    has_press = str_detect(type, 'Press')
  ) %>%
  arrange(!has_press) %>%
  pull(cite) %>%
  paste(collapse = ', ')
```


```{r}
#| results: asis

media %>%
  filter(highlight == 1) %>%
  pull(citation) %>%
  make_ordered_list()
```
