---
pagetitle: "Talks | Jubayer Hossain"
title: ""
page-layout: full
toc: false
comments: false
---

::: {.hero-section}
# Talks
A collection of invited talks, academic presentations, and conference contributions on bioinformatics, public health, and data science.
:::

::: {.main-content}

```{r}
#| echo: false
#| message: false
#| warning: false

# Load required libraries
library(yaml)

# Read talks data
talks_data <- yaml::read_yaml("../_data/talks.yml")

# Function to render talk card
render_talk_card <- function(talk) {
  # Create action buttons
  buttons_html <- ""
  if (!is.null(talk$slides)) {
    buttons_html <- paste0(buttons_html, '<a href="', talk$slides, '" class="talk-btn" target="_blank">View Slides</a>')
  }
  if (!is.null(talk$video)) {
    buttons_html <- paste0(buttons_html, '<a href="', talk$video, '" class="talk-btn" target="_blank">Watch Video</a>')
  }

  return(paste0(
    '<div class="talk-card">',
    '<div class="talk-header">',
    '<div class="talk-type">', talk$type, '</div>',
    '<div class="talk-date">', talk$date, '</div>',
    '</div>',
    '<div class="talk-content">',
    '<h3 class="talk-title">', talk$title, '</h3>',
    '<div class="talk-venue">',
    '<strong>', talk$venue, '</strong>',
    '<span class="talk-location">', talk$location, '</span>',
    '</div>',
    '<p class="talk-description">', talk$description, '</p>',
    if(buttons_html != "") paste0('<div class="talk-actions">', buttons_html, '</div>') else '',
    '</div>',
    '</div>'
  ))
}

```

## Talks

```{r}
#| echo: false
#| results: asis

# Sort talks by year (descending) and render
sorted_talks <- talks_data$talks[order(sapply(talks_data$talks, function(x) x$year), decreasing = TRUE)]

cat('<div class="talks-container">')
for (talk in sorted_talks) {
  cat(render_talk_card(talk))
}
cat('</div>')
```

:::

<style>
/* ===== HERO SECTION (PRESERVED) ===== */
.hero-section {
  text-align: center;
  padding: 3rem 1rem;
  margin-bottom: 2rem;
}

.hero-section h1 {
  font-size: 3rem;
  margin-bottom: 1rem;
  color: var(--text-primary);
}

.hero-section p {
  font-size: 1.2rem;
  color: var(--text-secondary);
  max-width: 600px;
  margin: 0 auto;
}

.main-content {
  max-width: 1200px;
  margin: 0 auto;
  padding: 0 1rem;
}

/* ===== TALKS CONTAINER ===== */
.talks-container {
  display: grid;
  grid-template-columns: repeat(auto-fit, minmax(420px, 1fr));
  gap: 2rem;
  margin-top: 2rem;
}

/* ===== PROFESSIONAL TALK CARDS ===== */
.talk-card {
  background: var(--bg-primary);
  border: 1px solid #e5e7eb;
  border-radius: 12px;
  overflow: hidden;
  transition: all 0.3s cubic-bezier(0.4, 0, 0.2, 1);
  box-shadow: 0 1px 3px 0 rgba(0, 0, 0, 0.1), 0 1px 2px 0 rgba(0, 0, 0, 0.06);
  position: relative;
}

.talk-card::before {
  content: '';
  position: absolute;
  top: 0;
  left: 0;
  right: 0;
  height: 4px;
  background: linear-gradient(90deg, #3b82f6, #1d4ed8);
}

.talk-card:hover {
  transform: translateY(-4px);
  box-shadow: 0 20px 25px -5px rgba(0, 0, 0, 0.1), 0 10px 10px -5px rgba(0, 0, 0, 0.04);
  border-color: #d1d5db;
}

/* ===== CARD HEADER ===== */
.talk-header {
  padding: 1.5rem 1.5rem 0 1.5rem;
  display: flex;
  justify-content: space-between;
  align-items: flex-start;
  gap: 1rem;
}

.talk-type {
  background: linear-gradient(135deg, #f8fafc, #e2e8f0);
  color: #475569;
  padding: 0.375rem 0.875rem;
  border-radius: 20px;
  font-size: 0.8rem;
  font-weight: 600;
  text-transform: uppercase;
  letter-spacing: 0.5px;
  border: 1px solid #e2e8f0;
}

.talk-date {
  background: #3b82f6;
  color: white;
  padding: 0.375rem 0.875rem;
  border-radius: 6px;
  font-size: 0.8rem;
  font-weight: 600;
  white-space: nowrap;
  box-shadow: 0 2px 4px rgba(59, 130, 246, 0.2);
}

/* ===== CARD CONTENT ===== */
.talk-content {
  padding: 1rem 1.5rem 1.5rem 1.5rem;
}

.talk-title {
  font-size: 1.375rem;
  font-weight: 700;
  color: #111827;
  margin: 0 0 1rem 0;
  line-height: 1.4;
  letter-spacing: -0.025em;
}

.talk-venue {
  margin-bottom: 1rem;
  padding: 0.75rem;
  background: #f9fafb;
  border-radius: 8px;
  border-left: 4px solid #3b82f6;
}

.talk-venue strong {
  color: #1f2937;
  font-weight: 600;
  font-size: 1rem;
  display: block;
  margin-bottom: 0.25rem;
}

.talk-location {
  color: #6b7280;
  font-size: 0.875rem;
  font-weight: 500;
}

.talk-description {
  color: #4b5563;
  line-height: 1.6;
  margin: 0 0 1.5rem 0;
  font-size: 0.95rem;
}

/* ===== CARD FOOTER ===== */
.talk-actions {
  display: flex;
  gap: 0.75rem;
  padding-top: 1rem;
  border-top: 1px solid #f3f4f6;
}

.talk-btn,
a.talk-btn,
.talk-btn * {
  background: linear-gradient(135deg, #3b82f6, #2563eb);
  color: #ffffff !important;
  padding: 0.75rem 1.25rem;
  border-radius: 8px;
  text-decoration: none !important;
  font-size: 0.875rem;
  font-weight: 600;
  transition: all 0.2s ease;
  border: none;
  cursor: pointer;
  display: inline-flex;
  align-items: center;
  gap: 0.5rem;
  box-shadow: 0 2px 4px rgba(59, 130, 246, 0.2);
  text-shadow: none;
}

.talk-btn:hover,
a.talk-btn:hover,
.talk-btn:hover * {
  background: linear-gradient(135deg, #2563eb, #1d4ed8);
  color: #ffffff !important;
  text-decoration: none !important;
  transform: translateY(-1px);
  box-shadow: 0 4px 8px rgba(59, 130, 246, 0.3);
}

.talk-btn:visited,
a.talk-btn:visited,
.talk-btn:visited * {
  color: #ffffff !important;
  text-decoration: none !important;
}

.talk-btn:focus,
a.talk-btn:focus,
.talk-btn:focus * {
  color: #ffffff !important;
  text-decoration: none !important;
  outline: 2px solid #93c5fd;
  outline-offset: 2px;
}

.talk-btn:active,
a.talk-btn:active,
.talk-btn:active * {
  color: #ffffff !important;
  text-decoration: none !important;
}

.talk-btn::before {
  content: "📄";
  font-size: 0.875rem;
}

/* ===== ENHANCED VISUAL ELEMENTS ===== */
.talk-card:nth-child(2n) .talk-type {
  background: linear-gradient(135deg, #f0f9ff, #dbeafe);
  color: #1e40af;
  border-color: #dbeafe;
}

.talk-card:nth-child(3n) .talk-type {
  background: linear-gradient(135deg, #f0fdf4, #dcfce7);
  color: #166534;
  border-color: #dcfce7;
}

/* ===== RESPONSIVE DESIGN ===== */
@media (max-width: 768px) {
  .hero-section h1 {
    font-size: 2rem;
  }

  .talks-container {
    grid-template-columns: 1fr;
    gap: 1.5rem;
  }

  .talk-header {
    flex-direction: column;
    align-items: flex-start;
    gap: 0.75rem;
  }

  .talk-title {
    font-size: 1.25rem;
  }

  .talk-actions {
    flex-direction: column;
  }

  .talk-btn {
    justify-content: center;
    width: 100%;
  }
}

@media (max-width: 480px) {
  .main-content {
    padding: 0 0.75rem;
  }

  .talk-card {
    border-radius: 8px;
  }

  .talk-header {
    padding: 1rem 1rem 0 1rem;
  }

  .talk-content {
    padding: 0.75rem 1rem 1rem 1rem;
  }

  .talk-venue {
    padding: 0.5rem;
  }

  .talk-title {
    font-size: 1.125rem;
  }
}

/* ===== LOADING ANIMATION ===== */
@keyframes fadeIn {
  from {
    opacity: 0;
    transform: translateY(20px);
  }
  to {
    opacity: 1;
    transform: translateY(0);
  }
}

.talk-card {
  animation: fadeIn 0.6s ease-out;
}

.talk-card:nth-child(1) { animation-delay: 0.1s; }
.talk-card:nth-child(2) { animation-delay: 0.2s; }
.talk-card:nth-child(3) { animation-delay: 0.3s; }
.talk-card:nth-child(4) { animation-delay: 0.4s; }
.talk-card:nth-child(5) { animation-delay: 0.5s; }
</style>
