---
pagetitle: "Teaching | Jubayer Hossain"
page-layout: full
comments: false
---

::: {.hero-section}
# Teaching
A collection of courses, workshops, and educational resources.
:::

::: {.main-content}

```{r}
#| echo: false
#| message: false
#| warning: false

# Load required libraries
library(yaml)

# Read teaching data
teaching_data <- yaml::read_yaml("../_data/teaching.yml")

# Function to render course card
render_course_card <- function(course) {
  # Get course type
  course_type <- if(!is.null(course$type)) course$type else "Course"

  # Create CSS class for course type
  type_class <- tolower(course_type)

  # Create links section
  links <- ""
  if (!is.null(course$syllabus)) {
    links <- paste0(links, '<a href="', course$syllabus, '" target="_blank" class="course-link">Syllabus</a>')
  }
  if (!is.null(course$slides)) {
    links <- paste0(links, '<a href="', course$slides, '" target="_blank" class="course-link">Slides</a>')
  }
  if (!is.null(course$code_repo)) {
    links <- paste0(links, '<a href="', course$code_repo, '" target="_blank" class="course-link">Code</a>')
  }

  paste0(
    '<div class="course-card">',
    '<div class="course-header">',
    '<span class="course-code">', course$course_id, '</span>',
    '<span class="course-type ', type_class, '">', course_type, '</span>',
    '</div>',
    '<h3 class="course-title">', course$title, '</h3>',
    '<p class="course-description">', course$learning_outcomes, '</p>',
    '<div class="course-links">',
    links,
    '</div>',
    '</div>'
  )
}
```

## Courses

```{r}
#| echo: false
#| results: asis

cat('<div class="courses-container">')

# Render all courses
for (course in teaching_data$courses) {
  cat(render_course_card(course))
}

cat('</div>')
```

:::

<style>
.hero-section {
  text-align: center;
  padding: 3rem 1rem;
  margin-bottom: 2rem;
}

.hero-section h1 {
  font-size: 3rem;
  margin-bottom: 1rem;
  color: var(--text-primary);
}

.hero-section p {
  font-size: 1.2rem;
  color: var(--text-secondary);
  max-width: 600px;
  margin: 0 auto;
}

.main-content {
  max-width: 1200px;
  margin: 0 auto;
  padding: 0 1rem;
}

.courses-container {
  display: grid;
  grid-template-columns: repeat(auto-fill, minmax(350px, 1fr));
  gap: 2rem;
  margin-top: 2rem;
}

.course-card {
  background: var(--bg-primary);
  border: 1px solid var(--border-light);
  border-radius: 8px;
  padding: 1.5rem;
  transition: all 0.3s ease;
}

.course-card:hover {
  transform: translateY(-2px);
  box-shadow: 0 4px 12px var(--shadow-light);
  border-color: var(--primary-color);
}

.course-header {
  display: flex;
  justify-content: space-between;
  align-items: center;
  margin-bottom: 1rem;
}

.course-code {
  background: #3b82f6;
  color: white;
  padding: 0.5rem 1rem;
  border-radius: 6px;
  font-size: 1rem;
  font-weight: 700;
  letter-spacing: 0.5px;
}

.course-type {
  background: var(--bg-muted);
  color: var(--text-secondary);
  padding: 0.25rem 0.75rem;
  border-radius: 4px;
  font-size: 0.9rem;
  border: 1px solid var(--border-light);
}

.course-type.workshop {
  background: linear-gradient(135deg, #10b981, #059669);
  color: white;
  border: none;
}

.course-type.seminar {
  background: linear-gradient(135deg, #f59e0b, #d97706);
  color: white;
  border: none;
}

.course-type.webinar {
  background: linear-gradient(135deg, #8b5cf6, #7c3aed);
  color: white;
  border: none;
}

.course-title {
  font-size: 1.25rem;
  margin: 0 0 1rem 0;
  color: var(--text-primary);
  line-height: 1.3;
}

.course-description {
  color: var(--text-secondary);
  line-height: 1.5;
  margin: 0 0 1.5rem 0;
}

.course-links {
  display: flex;
  gap: 0.75rem;
  flex-wrap: wrap;
}

.course-link {
  background: #6366f1;
  color: white;
  padding: 0.5rem 1rem;
  border-radius: 4px;
  text-decoration: none;
  font-size: 0.9rem;
  transition: all 0.2s ease;
  margin-right: 0.5rem;
}

.course-link:hover {
  background: #4f46e5;
  color: white;
  text-decoration: none;
  transform: translateY(-1px);
}

@media (max-width: 768px) {
  .hero-section h1 {
    font-size: 2rem;
  }

  .courses-container {
    grid-template-columns: 1fr;
    gap: 1.5rem;
  }

  .course-header {
    flex-direction: column;
    gap: 0.5rem;
    align-items: flex-start;
  }
}
</style>
