---
pagetitle: "Media Coverage | Jubayer Hossain"
title: ""
page-layout: full
toc: false
comments: false
---

::: {.hero-section}
# Media Coverage
Explore the latest media highlights featuring me and my research group. Discover insightful coverage of their impactful research.
:::

::: {.main-content}

```{r}
#| echo: false
#| message: false
#| warning: false

# Load required libraries
library(yaml)

# Read press data
press_data <- yaml::read_yaml("../_data/press.yml")

# Function to render media card
render_media_card <- function(media) {
  # Get category info
  category_info <- press_data$categories[sapply(press_data$categories, function(x) x$name == media$category)][[1]]
  category_color <- if(!is.null(category_info$color)) category_info$color else "#6366f1"
  category_icon <- if(!is.null(category_info$icon)) category_info$icon else "📰"

  # Get media type info
  type_info <- press_data$media_types[sapply(press_data$media_types, function(x) x$name == media$type)][[1]]
  type_icon <- if(!is.null(type_info$icon)) type_info$icon else "📰"


  # Create tags
  tags_html <- ""
  if (!is.null(media$tags) && length(media$tags) > 0) {
    tags_list <- paste0('<span class="media-tag">', media$tags, '</span>', collapse = '')
    tags_html <- paste0('<div class="tags-container">', tags_list, '</div>')
  }

  # Determine card class
  card_class <- "media-card"

  return(paste0(
    '<div class="', card_class, '">',
    '<div class="media-header">',
    '<div class="media-type" style="background-color: ', category_color, '15; color: ', category_color, ';">',
    '<span class="type-icon">', type_icon, '</span>',
    '<span class="type-name">', media$type, '</span>',
    '</div>',
    '<div class="media-date">', media$date, '</div>',
    '</div>',
    '<div class="media-content">',
    '<h3 class="media-title">', media$title, '</h3>',
    '<div class="media-publication">',
    '<strong>', media$publication, '</strong>',
    '<span class="media-category"> • ', media$category, '</span>',
    '</div>',
    '<p class="media-summary">', media$summary, '</p>',
    tags_html,
    '<div class="media-actions">',
    '<a href="', media$link, '" class="media-btn" target="_blank">Read Article</a>',
    '</div>',
    '</div>',
    '</div>'
  ))
}
```

## Recent Media Coverage

```{r}
#| echo: false
#| results: asis

# Sort media coverage by date (most recent first)
sorted_media <- press_data$media_coverage[order(as.Date(sapply(press_data$media_coverage, function(x) x$date), format = "%d %B %Y"), decreasing = TRUE)]

cat('<div class="media-container">')
for (media in sorted_media) {
  cat(render_media_card(media))
}
cat('</div>')
```

:::

<style>
/* ===== HERO SECTION (PRESERVED) ===== */
.hero-section {
  text-align: center;
  padding: 3rem 1rem;
  margin-bottom: 2rem;
}

.hero-section h1 {
  font-size: 3rem;
  margin-bottom: 1rem;
  color: var(--text-primary);
}

.hero-section p {
  font-size: 1.2rem;
  color: var(--text-secondary);
  max-width: 600px;
  margin: 0 auto;
}

.main-content {
  max-width: 1200px;
  margin: 0 auto;
  padding: 0 1rem;
}

/* ===== MEDIA CONTAINER ===== */
.media-container {
  display: grid;
  grid-template-columns: repeat(auto-fit, minmax(450px, 1fr));
  gap: 2rem;
  margin-top: 2rem;
}

/* ===== PROFESSIONAL MEDIA CARDS ===== */
.media-card {
  background: var(--bg-primary);
  border: 1px solid #e5e7eb;
  border-radius: 12px;
  overflow: hidden;
  transition: all 0.3s cubic-bezier(0.4, 0, 0.2, 1);
  box-shadow: 0 1px 3px 0 rgba(0, 0, 0, 0.1), 0 1px 2px 0 rgba(0, 0, 0, 0.06);
  position: relative;
}

.media-card::before {
  content: '';
  position: absolute;
  top: 0;
  left: 0;
  right: 0;
  height: 4px;
  background: linear-gradient(90deg, #3b82f6, #1d4ed8);
}

.media-card:hover {
  transform: translateY(-3px);
  box-shadow: 0 10px 25px -3px rgba(0, 0, 0, 0.1), 0 4px 6px -2px rgba(0, 0, 0, 0.05);
  border-color: #d1d5db;
}


/* ===== MEDIA HEADER ===== */
.media-header {
  padding: 1.5rem 1.5rem 0 1.5rem;
  display: flex;
  justify-content: space-between;
  align-items: flex-start;
  gap: 1rem;
}

.media-type {
  display: flex;
  align-items: center;
  gap: 0.5rem;
  padding: 0.5rem 1rem;
  border-radius: 20px;
  font-size: 0.8rem;
  font-weight: 600;
  text-transform: uppercase;
  letter-spacing: 0.5px;
  border: 1px solid currentColor;
}

.type-icon {
  font-size: 1rem;
}

.media-date {
  background: #374151;
  color: white;
  padding: 0.375rem 0.875rem;
  border-radius: 6px;
  font-size: 0.8rem;
  font-weight: 600;
  white-space: nowrap;
  box-shadow: 0 2px 4px rgba(55, 65, 81, 0.2);
}

/* ===== MEDIA CONTENT ===== */
.media-content {
  padding: 1rem 1.5rem 1.5rem 1.5rem;
}

.media-title {
  font-size: 1.25rem;
  font-weight: 700;
  color: #111827;
  margin: 0 0 1rem 0;
  line-height: 1.4;
  letter-spacing: -0.025em;
}

.media-publication {
  margin-bottom: 1rem;
  padding: 0.75rem;
  background: #f8fafc;
  border-radius: 8px;
  border-left: 4px solid #3b82f6;
}

.media-publication strong {
  color: #1f2937;
  font-weight: 700;
  font-size: 1rem;
}

.media-category {
  color: #6b7280;
  font-size: 0.875rem;
  font-weight: 500;
}

.media-summary {
  color: #4b5563;
  line-height: 1.6;
  margin: 0 0 1.5rem 0;
  font-size: 0.95rem;
}

/* ===== MEDIA TAGS ===== */
.tags-container {
  display: flex;
  flex-wrap: wrap;
  gap: 0.5rem;
  margin-bottom: 1.5rem;
}

.media-tag {
  background: #f3f4f6;
  color: #374151;
  padding: 0.25rem 0.75rem;
  border-radius: 12px;
  font-size: 0.75rem;
  font-weight: 500;
  border: 1px solid #e5e7eb;
  transition: all 0.2s ease;
}

.media-tag:hover {
  background: #3b82f6;
  color: white;
  border-color: #3b82f6;
}

/* ===== MEDIA ACTIONS ===== */
.media-actions {
  padding-top: 1rem;
  border-top: 1px solid #f3f4f6;
}

.media-btn,
a.media-btn,
.media-btn * {
  background: linear-gradient(135deg, #3b82f6, #2563eb);
  color: #ffffff !important;
  padding: 0.75rem 1.5rem;
  border-radius: 8px;
  text-decoration: none !important;
  font-size: 0.875rem;
  font-weight: 600;
  transition: all 0.2s ease;
  border: none;
  cursor: pointer;
  display: inline-flex;
  align-items: center;
  gap: 0.5rem;
  box-shadow: 0 2px 4px rgba(59, 130, 246, 0.2);
  text-shadow: none;
}

.media-btn:hover,
a.media-btn:hover,
.media-btn:hover * {
  background: linear-gradient(135deg, #2563eb, #1d4ed8);
  color: #ffffff !important;
  text-decoration: none !important;
  transform: translateY(-1px);
  box-shadow: 0 4px 8px rgba(59, 130, 246, 0.3);
}

.media-btn:visited,
a.media-btn:visited,
.media-btn:visited * {
  color: #ffffff !important;
  text-decoration: none !important;
}

.media-btn:focus,
a.media-btn:focus,
.media-btn:focus * {
  color: #ffffff !important;
  text-decoration: none !important;
  outline: 2px solid #93c5fd;
  outline-offset: 2px;
}

.media-btn::before {
  content: "📰";
  font-size: 0.875rem;
}

/* ===== RESPONSIVE DESIGN ===== */
@media (max-width: 768px) {
  .hero-section h1 {
    font-size: 2rem;
  }

  .media-container {
    grid-template-columns: 1fr;
    gap: 1.5rem;
  }

  .media-header {
    flex-direction: column;
    align-items: flex-start;
    gap: 0.75rem;
  }

  .media-title {
    font-size: 1.125rem;
  }

  .media-actions {
    text-align: center;
  }

  .media-btn {
    width: 100%;
    justify-content: center;
  }
}

@media (max-width: 480px) {
  .main-content {
    padding: 0 0.75rem;
  }

  .media-card {
    border-radius: 8px;
  }

  .media-header {
    padding: 1rem 1rem 0 1rem;
  }

  .media-content {
    padding: 0.75rem 1rem 1rem 1rem;
  }

  .media-publication {
    padding: 0.5rem;
  }

  .media-title {
    font-size: 1rem;
  }
}

/* ===== LOADING ANIMATION ===== */
@keyframes fadeInUp {
  from {
    opacity: 0;
    transform: translateY(30px);
  }
  to {
    opacity: 1;
    transform: translateY(0);
  }
}

.media-card {
  animation: fadeInUp 0.6s ease-out;
}

.media-card:nth-child(1) { animation-delay: 0.1s; }
.media-card:nth-child(2) { animation-delay: 0.2s; }
.media-card:nth-child(3) { animation-delay: 0.3s; }
.media-card:nth-child(4) { animation-delay: 0.4s; }
.media-card:nth-child(5) { animation-delay: 0.5s; }
</style>

